%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Researcher} % Affiliation/role
    {Excellence Program in Microelectronic} % Organization/group
    {Brazil} % Location
    {Sep. 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Gaining expertise in Linux, Computer Architecture, and Digital System.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Secretary} % Affiliation/role
    {IFPB ACM Student Chapter} % Organization/group
    {Brazil} % Location
    {Jun. 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Participation in the opening procedure of the first Brazilian ACM Student Chapter.}
        \item {Development of soft skills.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Competitor Member \& Stuff} % Affiliation/role
    {IFPB Olympic Programming Project (POP)} % Organization/group
    {Brazil} % Location
    {Jan. 2015 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Participation in problem solving competition, obtaining good awards.}
        \item {Gained expertise in organizing problem solving competitions}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Member Volunteer} % Affiliation/role
    {IFPB IEEE Student Branch} % Organization/group
    {Brazil} % Location
    {Feb. 2014 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Development in leadership, communication, verbal, adversities solution skills and other soft skills.}
        \item {Gained expertise in organizing events and writing reports.}
        \item {Increased technical skills doing undergraduate researches.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Member Volunteer} % Affiliation/role
    {IFPB IEEE WIE Affinity Group} % Organization/group
    {Brazil} % Location
    {Feb. 2014 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Gained expertise in engaging women for STEAM fields.}
        \item {Gained experience in developing social inclusion activities.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
